---
title: "Using promor for label-free quantification proteomics data analysis"
author: "Chathurani Ranathunge"
date: "`r Sys.Date()`"

output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using promor for label-free quantification proteomics data analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = TRUE}
library(promor)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This tutorial shows how to analyze label-free quantification data (LFQ)
using *promor*. We use a publicly available data set (PXD000279) downloaded from the PRIDE archive as an example for a data set that does not contain 
technical replicates.  


## Get started
Below we are showing a simple example, illustrating the functionality of 
*promor*.

### 1. First create a raw.df object.
You will need a "proteinGroups.txt" file produced by *MaxQuant* and an 
experimental design file. An example experimental design file can be found here:

```{r quick_start, eval=FALSE}
library(promor)
raw <- create.df(file.path = "./proteinGroups.txt", 
                 exp.design = "./exp_design.txt")

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
